Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-12 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:12	17:45:00	(Wed12.Aug)

Compared to conventional methods, MVDR is often able to improve image contrast and resolution, as shown in~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}.

>>>>

MVDR is often able to improve image contrast and resolution compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, it is computationally intensive, needs robustification to work well, and should be used on images that are oversampled 10 times in azimuth.

In prior studies we have investigated ways to reduce the complexity of MVDR and accelerate it using graphics computing units (GPUs)~\cite{Buskenes2014,Aasen2013}.
